### 2018-06-04 Paper_vi_VN.tex
first draft version of yellow paper in Vietnamese

% !TEX encoding = UTF-8 Unicode

\documentclass[12pt]{amsart}
\usepackage{cancel}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[a4paper,width=170mm,top=18mm,bottom=22mm,includeheadfoot]{geometry}
\usepackage{array}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{natbib}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{mathtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{afterpage}
\usepackage{tikz}
\usepackage[bookmarks=true, unicode=true, pdftitle={Nexty Yellow Paper: a formal specification of Nexty, a zero transfer fee and instant transfer base on Ethereum blockchain}, pdfauthor={Thanh Dao / Ha Dang},pdfkeywords={Nexty, Ethereum, Yellow Paper, blockchain, virtual machine, cryptography, decentralised, singleton, transaction, generalised, zero transfer fee, instant transfer},pdfborder={0 0 0.5 [1 3]}]{hyperref}
%,pagebackref=true

\usepackage{tabu} %requires array.

\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}

\definecolor{pagecolor}{rgb}{1,0.98,0.9}

\title{NEXTY: AN ALTERNATIVE CONSENSUS TO GET ZERO TRANSFER FEE AND INSTANT TRANSFER FROM ETHEREUM BLOCKCHAIN}
\author{
	Thanh Dao / Ha Dang \\
	CO-FOUNDER/CTO NEXTY PLATFORM \\
	thanhdao@nexty.io
}
\date{} % delete this line to display the current date

%%% BEGIN DOCUMENT
\begin{document}

\pagecolor{pagecolor}
\begin{abstract}
Đây là phần mô tả mang tính kỹ thuật của Nexty Platform, tập trung vào việc chi tiết cách thức vận hành của Consensus Protocol tên là Proof of Foundation (Algorithm name: DCCS - Dual Cryptocurrency Confirmation System). Proof of Foundation được inspired từ Proof of Authority được đề xuất bởi \cite{clique}, nhưng vận hành theo DCCS để có được tính decentralized hoàn thiện hơn và đồng thời mang lại sự incentive cho những người duy trì blockchain.
\end{abstract}

\maketitle

\setlength{\columnsep}{20pt}
\begin{multicols}{2}
%\tableofcontents

\section{Mô tả chung}\label{sec:introduction}
DCCS là hệ thống có thêm 1 token thứ 2 tên là NTF ngoài NTY. NTF là token dùng để xác định Authorities duy trì confirmation system, đồng thời cũng xác định số lượng trả thưởng cho việc đóng Blocks. NTF là token có số lượng 10,000,000 được tặng tương ứng với 100,000,000,000 NTY đầu tiên tham gia chương trình smart staking của Nexty, hay có thể nói là những người đầu tiên có tầm nhìn và tâm huyết với hệ thống của Nexty. Chính vì thế Consensus Protocol được đặt tên là Proof of Foundation. Tuy nhiên, sức mạnh của hệ thống lại không nằm ở những người sở hữu NTF vì họ có thể bị vote down trong những trường hợp như phát hiện gian lận, quá centralized, hay không cập nhật kịp thời những source code mới từ hệ thống. Chính vì vậy, ở một khía cạnh khác có thể nói những người sở hữu NTF là những người đi làm thuê cho hệ thống, và bản thân họ không phải là những người chủ thực sự của Nexty Blockchain. Đây là một decentralized system mới, được duy trì từ những người sở hữu NTY.

\section{Cách thức authorize một account được trở thành block sealer}
Hệ thống sẽ đặt ra parametter xem giá trị tối thiểu mà địa chỉ NTF phải có để có thể trở thành 1 sealer. Sẽ có 1 smart contract, trong đó chỉ định gán quyền của 1 địa chỉ NTF với số lượng token lớn hơn min-ntf, sang 1 địa chỉ Account khác gọi là executing-account với giá trị state là authorized-sealer với giá trị bằng địa chỉ của NTF. Nếu 1 địa chỉ đã tồn tại 1 giá trị authorized-sealer thì nó ko thể nhận authorization từ 1 NTF holder nào khác cho đến khi NTF holder đó tạo lệnh withdraw từ authorized-sealer. Lệnh đặt authorized-sealer phải được thực hiện sau khi cài đặt và vận hành sealing node để có thể tham gia vào sealing round tiếp theo. Trường hợp nếu trong 1 sealing round, authorized-sealer không thực hiện 1 sealing activity thì giá trị authorized-sealer sẽ bị withdraw về NTF holder của nó và tất nhiên không được tham gia vào sealing round tiếp theo cho đến khi được authorize trở lại.

\section{Cách thức các sealers đóng block}
Cách thức đóng Block của DCCS là các sealers sẽ được đánh số từ 1 đến n (gọi là sealing-id) một cách ngẫu nhiên theo từng sealing round: trong đó n là số lượng các authorized-sealers đã được đăng ký.

\subsection{Trường hợp 1} Nếu sealing node không nằm trong recent sealers. Nếu số dư bằng chính sealing-id thì node đó được quyền seal block ngay lập tức. Đối với số dư khác sealing-id, ở mỗi block tiếp theo, các sealing node phải tự xác định thời gian chờ được tính như sau:

\bibliographystyle{plainnat}
\bibliography{Biblio}

\end{multicols}
\end{document}

### 2018-06-05 Paper_vi_VN.tex
Add some more sectiions and formula

@@
 \PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
+
+\makeatletter
+ \newcommand{\linkdest}[1]{\Hy@raisedlink{\hypertarget{#1}{}}}
+\makeatother
+\usepackage{seqsplit}
 
@@
 NTF là token dùng để xác định Authorities duy trì confirmation system, đồng thời cũng xác định số lượng trả thưởng cho việc đóng Blocks.
-NTF là token có số lượng 10,000,000 được tặng tương ứng với 100,000,000,000 NTY đầu tiên tham gia chương trình smart staking của Nexty, hay có thể nói là những người đầu tiên có tầm nhìn và tâm huyết với hệ thống của Nexty.
-Chính vì thế Consensus Protocol được đặt tên là Proof of Foundation.
-Tuy nhiên, sức mạnh của hệ thống lại không nằm ở những người sở hữu NTF vì họ có thể bị vote down trong những trường hợp như phát hiện gian lận, quá centralized, hay không cập nhật kịp thời những source code mới từ hệ thống.
-Chính vì vậy, ở một khía cạnh khác có thể nói những người sở hữu NTF là những người đi làm thuê cho hệ thống, và bản thân họ không phải là những người chủ thực sự của Nexty Blockchain.
-Đây là một decentralized system mới, được duy trì từ những người sở hữu NTY.
+NTF là token có số lượng 10,000,000 được tặng tương ứng với 100,000,000,000 NTY đầu tiên tham gia chương trình smart staking đã được mô tả chi tiết trong whitepaper của \cite{smart-taking}, hay có thể nói là những người đầu tiên có tầm nhìn và tâm huyết với hệ thống của Nexty.
+Chính vì thế consensus protocol được đặt tên là Proof of Foundation.
+Tuy nhiên, sức mạnh của hệ thống lại không nằm ở những người sở hữu NTF vì họ có thể bị vote down trong những trường hợp như phát hiện gian lận, quá centralized, hay không cập nhật kịp thời source code mới từ hệ thống.
+Chính vì vậy, ở một khía cạnh khác có thể nói những người sở hữu NTF là những người đi làm thuê cho hệ thống, và bản thân họ không phải là những người chủ thực sự của Nexty blockchain.
+Đây là một decentralized system mới, được duy trì bởi cộng đồng người dùng sở hữu NTY.
 
 \section{Cách thức authorize một account được trở thành block sealer}
-Hệ thống sẽ đặt ra parametter xem giá trị tối thiểu mà địa chỉ NTF phải có để có thể trở thành 1 sealer.
-Sẽ có 1 smart contract, trong đó chỉ định gán quyền của 1 địa chỉ NTF với số lượng token lớn hơn min-ntf, sang 1 địa chỉ Account khác gọi là executing-account với giá trị state là authorized-sealer với giá trị bằng địa chỉ của NTF.
-Nếu 1 địa chỉ đã tồn tại 1 giá trị authorized-sealer thì nó ko thể nhận authorization từ 1 NTF holder nào khác cho đến khi NTF holder đó tạo lệnh withdraw từ authorized-sealer.
-Lệnh đặt authorized-sealer phải được thực hiện sau khi cài đặt và vận hành sealing node để có thể tham gia vào sealing round tiếp theo.
-Trường hợp nếu trong 1 sealing round, authorized-sealer không thực hiện 1 sealing activity thì giá trị authorized-sealer sẽ bị withdraw về NTF holder của nó và tất nhiên không được tham gia vào sealing round tiếp theo cho đến khi được authorize trở lại.
+Hệ thống sẽ đặt ra một config parametter để xác định giá trị tối thiểu min-ntf mà một địa chỉ NTF cần phải có để có thể trở thành block sealer.
+Nexty sẽ xây dựng và phát triển một smart contract, trong đó chỉ định gán quyền của một địa chỉ NTF với số lượng token lớn hơn min-ntf, sang một địa chỉ Account khác gọi là executing-account với giá trị state là authorized-sealer với giá trị bằng địa chỉ của NTF.
+Nếu một địa chỉ đã tồn tại một giá trị authorized-sealer thì nó ko thể nhận authorization từ một NTF holder nào khác cho đến khi NTF holder đó tạo lệnh withdraw từ authorized-sealer.
+Lệnh đặt authorized-sealer phải được thực hiện sau khi cài đặt và vận hành sealing node bằng cách đọc state từ smart contract để có thể xác định danh sách authorized-sealer được tham gia vào sealing round tiếp theo.
+Trường hợp nếu trong sealing round hiện tại, authorized-sealer không thực hiện 1 sealing activity thì giá trị authorized-sealer sẽ bị withdraw về NTF holder của nó bằng cách thay đổi state của smart contract tại checkpoint block number của sealing round tiếp theo và tất nhiên authorized-sealer đó sẽ không được tham gia vào sealing round tiếp theo cho đến khi được authorize trở lại.
 
 \section{Cách thức các sealers đóng block}
-Cách thức đóng Block của DCCS là các sealers sẽ được đánh số từ 1 đến n (gọi là sealing-id) một cách ngẫu nhiên theo từng sealing round: trong đó n là số lượng các authorized-sealers đã được đăng ký.
+Cách thức đóng Block của DCCS là các sealers sẽ được đánh số từ $1$ đến $n$ (gọi là ``sealing-id'') một cách ngẫu nhiên theo từng sealing round: trong đó $n$ là số lượng các authorized-sealers đã được đăng ký và được xác định từ state của smart contract tại checkpoint block number của sealing round tương ứng.
+Để đảm bảo tính ngẫu nhiên khi đánh số ``sealing-id'', thì việc đánh số theo mã hash, $\boldsymbol{\xi_{\mathrm{k}}}$, được tính toán theo công thức sau đây khi bắt đầu một sealing round mới.
+\begin{equation}
+\xi_{\mathrm{k}} \equiv \texttt{\small KEC}(\mathbf{block}, \mathbf{\Lambda_{\mathrm{k}}})
+\end{equation}
 
-\subsection{Trường hợp 1} Nếu sealing node không nằm trong recent sealers.
-Nếu số dư bằng chính sealing-id thì node đó được quyền seal block ngay lập tức.
-Đối với số dư khác sealing-id, ở mỗi block tiếp theo, các sealing node phải tự xác định thời gian chờ được tính như sau:
+\begin{description}
+\item[block] là block number đầu tiên, a.k.a checkpoint block number, của sealing round
+\item[$\Lambda_{\mathrm{k}}$] là địa chỉ ví mà NTF holder đã thiết định để làm authorized-sealer trong smart contract.
+\item[\texttt{\small KEC}] là hàm tính băm của một input bất kỳ theo thuật toán \textbf{SHA-3 Keccak-512}.
+\end{description}
+
+Sau đó, ``sealing-id'' của từng authorized-sealer sẽ được lấy bằng vị trí của \textit{sealing hash}, $\boldsymbol{\xi_k}$, trong array $(\xi_{\mathrm{1}}, \xi_{\mathrm{2}}, ..., \xi_{\mathrm{n}})$ đã được sắp xếp theo thứ tự tăng dần theo \textit{sealing hash} của toàn bộ các authorized-sealers tại sealing round hiện thời.
+
+Để đảm bảo performance của hệ thống thì ``sealing-id'' của toàn bộ authorised sealer sẽ được snapshot duy nhất một lần từ state của smart contract tại checkpoint block number của mỗi sealing round và lưu vào \textbf{lru cache} của từng node.
+
+\subsection{Trường hợp 1} Nếu sealing node không nằm trong recent sealers. Node sẽ xác định block tiếp theo có phải là đến lượt nó làm sealer hay không theo công thức sau:
+
+\begin{equation}
+\sigma_{\mathrm{k}} \equiv (\nu - \mathbf{block}) \ \ \ \mathbf{mod} \ \ \ \Pi
+\end{equation}
+
+\begin{description}
+\item[$\nu$] là block number hiện tại sẽ được seal.
+\item[block] là block number đầu tiên, a.k.a checkpoint block number, của sealing round
+\item[$\Pi$] tổng số authorised sealer đã được xác định tại checkpoint block của sealing round hiện tại.
+\end{description}
+
+Nếu số dư $\sigma_{\mathrm{k}}$ bằng chính ``sealing-id'' của node thì node đó được quyền seal block ngay lập tức.
+Đối với số dư khác với ``sealing-id'', ở mỗi block tiếp theo, các sealing node phải tự xác định thời gian chờ, $\psi_{\mathrm{k}}$, được tính như sau:
+
+\begin{equation}
+\psi_{\mathrm{k}} \equiv \sum_{i=1}^{\zeta_\mathrm{k}} \mathbf{floor}(\frac{\alpha}{\beta*i+\gamma} + \delta)
+\end{equation}
 

### 2018-06-05 Paper_vi_VN.tex
Add parameter value for sealer waiting time formula
Add multiline equation for better view layout

@@
 \usepackage{seqsplit}
+
+% For formatting
+%\usepackage{underscore}
+%\usepackage{lipsum} % to generate filler text for testing of document rendering
+\usepackage[english]{babel}
+\usepackage[autostyle]{csquotes}
+\MakeOuterQuote{"}
 
@@
 
-\begin{equation}
+\begin{eqnarray}
+\alpha = 1.387978 \\
+\beta = 0.002313279 \\
+\gamma = 0.00462659 \\
+\delta = 199.9994 \\
 \psi_{\mathrm{k}} \equiv \sum_{i=1}^{\zeta_\mathrm{k}} \mathbf{floor}(\frac{\alpha}{\beta*i+\gamma} + \delta)
-\end{equation}
+\end{eqnarray}
+
+\subsection{Trường hợp 2} Nếu sealing node nằm trong recent sealers
+
+Trường hợp này có thể cho sealers được tiếp tục seal, nhưng phải đợi hết 1 vòng khi không còn sealer không nằm trong recent sealers đang hoạt động.
+Đây là phương thức nhằm đảm bảo khi chỉ còn 1 sealer thì hệ thống vẫn có thể tạo block, tuy nhiên với thời gian rất lâu.
+Thời gian này rơi vào khoảng 3 - 30 phút nếu có từ 1000 - 10,000 authorized sealers nhưng chỉ có một hoặc rất ít active sealers.
+
+Thời gian chờ $\psi_{\mathrm{k}}$ được theo công thức sau:
+
+\begin{eqnarray}
+\alpha = 1.387978 \\
+\beta = 0.002313279 \\
+\gamma = 0.00462659 \\
+\delta = 199.9994
+\end{eqnarray}
+
+\begin{multline}
+\psi_{\mathrm{k}} \equiv \sum_{i=1}^{n} \mathbf{floor}(\frac{\alpha}{\beta*i+\gamma} + \delta) \\ 
++ \sum_{i=1}^{\zeta_\mathrm{k}} \mathbf{floor}(\frac{\alpha}{\beta*i+\gamma} + \delta)
+\end{multline}
 

### 2018-06-05 Paper_vi_VN.tex
Add image graphics for curve fitting

@@
 \definecolor{pagecolor}{rgb}{1,0.98,0.9}
+
+%Path relative to the main .tex file 
+\graphicspath{ {./images/} }
 
@@
 
-\begin{equation}
+\begin{equation}\label{eq:sigma}
 \sigma_{\mathrm{k}} \equiv (\nu - \mathbf{block}) \ \ \ \mathbf{mod} \ \ \ \Pi
@@
 \begin{eqnarray}
-\alpha = 1.387978 \\
-\beta = 0.002313279 \\
-\gamma = 0.00462659 \\
-\delta = 199.9994 \\
+\alpha = 001.387978000 \\
+\beta = 000.002313279 \\
+\gamma = 000.004626590 \\
+\delta = 199.999400000
+\end{eqnarray}
+
+\begin{equation}\label{eq:psi}
 \psi_{\mathrm{k}} \equiv \sum_{i=1}^{\zeta_\mathrm{k}} \mathbf{floor}(\frac{\alpha}{\beta*i+\gamma} + \delta)
-\end{eqnarray}
+\end{equation}
 
@@
 \begin{eqnarray}
-\alpha = 1.387978 \\
-\beta = 0.002313279 \\
-\gamma = 0.00462659 \\
-\delta = 199.9994
+\alpha = 001.387978000 \\
+\beta = 000.002313279 \\
+\gamma = 000.004626590 \\
+\delta = 199.999400000
 \end{eqnarray}
 
-\begin{multline}
+\begin{multline}\label{eq:psi_2}
 \psi_{\mathrm{k}} \equiv \sum_{i=1}^{n} \mathbf{floor}(\frac{\alpha}{\beta*i+\gamma} + \delta) \\ 
@@
 \end{multline}
+
+Cách thức xây dựng hệ số cho công thức trên được giả định như sau.
+Đối với sealing node có sealing-id trùng với số dư r, được tính theo công thức $\eqref{eq:sigma}$, thì được ưu tiên seal block trước 400ms, sealing node tiếp theo được ưu tiên 350ms, và sau đó lần lượt là 320… cho đến sealing node lớn hơn số dư một khoảng lớn nhất thì xấp xỉ 200ms.
+Đồ thị của nó sẽ tương ứng với hàm số $\texttt{\small y} = \frac{a} {(b * x + c)} + \texttt{\small d}$
+
+Để ước lượng giá trị cho các tham số của công thức này, chúng tôi sử dụng phương pháp curve fitting để tìm ra hệ số tương đối theo website \href{https://mycurvefit.com/}{My Curve Fit} với phương sai \footnote{R² is 1 minus the ratio of sum of the squares of the residuals divided by the sum of the squares of the differences between Y fit and the mean Y value} xấp xỉ bằng 1.
+\\
+\\
+\includegraphics[width=0.48\textwidth, height=4cm]{curve-fit}
+\\
 

### 2018-06-05 Paper_vi_VN.tex
first draft Vietnamese version of yellow paper

@@
 
-\documentclass[12pt]{amsart}
+\documentclass[12pt,oneside]{amsart}
 \usepackage{cancel}
@@
 \usepackage{amssymb}
-\usepackage[a4paper,width=170mm,top=18mm,bottom=22mm,includeheadfoot]{geometry}
+\usepackage[a4paper,width=165mm,top=20mm,bottom=25mm,includeheadfoot]{geometry}
 \usepackage{array}
@@
 %,pagebackref=true
-
-\usepackage{tabu} %requires array.
 
@@
 
-\title{NEXTY: AN ALTERNATIVE CONSENSUS TO GET ZERO TRANSFER FEE AND INSTANT TRANSFER FROM ETHEREUM BLOCKCHAIN}
+\title{NEXTY: A CONSENSUS TO GET ZERO TRANSFER FEE AND INSTANT TRANSFER BLOCKCHAIN}
 \author{
-	Thanh Dao / Ha Dang \\
+	Thanh Dao \& Ha Dang \\
 	CO-FOUNDER/CTO NEXTY PLATFORM \\
-	thanhdao@nexty.io
+	thanhdao@nexty.io / dvietha@gmail.com
 }
@@
 \\
+Mỗi một vòng đóng block của các sealers sẽ được gọi là một epoch. Tuỳ theo số lượng sealer trong chain của từng sealing round mà một epoch sẽ có độ dài khác nhau.
+
+Bằng phương thức tính thời gian chờ cố định cho từng sealers theo công thức  $\eqref{eq:psi}$ và $\eqref{eq:psi_2}$, consensus có thể kiểm tra được xem một sealer; vì lo ngại bị withdraw authorised sealer về NTF holder do không thực hiện sealing activity trong một sealing round mà chiếm quyền sealing block tại một thời điểm nào đó sớm hơn khi chưa đến lượt seal; gây ra sự hỗn loạn và racing for sealing block.
+Thuật toán đồng thuận của Nexty sẽ thực hiện verify một block được seal bởi một authorized sealer bằng cách kiểm tra lại xem thời gian sinh ra block của authorized-sealer đó có đúng nhỏ hơn thời gian nó phải chờ hay không.
+
+\section{Cách thức trả thưởng cho các sealers}
+
+Cứ sau mỗi sealing round, giá trị thưởng $\Re$ của mỗi sealer sẽ được tính bằng giá trị nhỏ nhất của tổng số lượng thưởng chia cho các active sealers theo tỷ lệ số lượng NTF họ có trên tổng số NTF của những người được làm sealers mà có tham gia quá trình seal.
+
+\begin{eqnarray}
+\theta = \frac{\Omega}{N} \\
+\phi = \frac{\Upsilon_{NTF}}{\Xi_{NTF}}
+\end{eqnarray}
+
+\begin{equation}\label{eq:re}
+\Re \equiv \mathbf{min}(\theta, \phi)
+\end{equation}
+
+\begin{description}
+\item[$\Omega$] total reward
+\item[N] total number of active sealer of the current sealing round
+\item[$\Upsilon_{NTF}$] amount of NTF token that the owner of active sealer is holding
+\item[$\Xi_{NTF}$] total amount of NTF token that all active sealer are holding
+\end{description}
+
+Bằng cách thức tính reward $\Re$ theo công thức $\eqref{eq:re}$, người sở hữu nhiều NTF theo một cách tự nhiên sẽ phân chia NTF của mình ra nhiều ví để trang bị nhiều máy làm sealer, thay vì chỉ build một máy sealer và tập trung quá nhiều NTF vào đó.
+Điều này đảm bảo Nexty chain sẽ có số lượng node đủ lớn để đảm bảo tính decentralise, tính ổn định và tăng độ chịu tải cho toàn bộ Nexty chain.
+
+Total reward $\Re$ là lượng NTY được sinh ra sau mỗi 1 sealing round, được tính bằng \textit{[số reward sinh ra 1 block]} * \textit{[số block được tạo ra ở sealing round đó]}
+
+Số reward sinh ra cho một block được bằng số reward trong một năm chia cho $\mathbf{15768000}$, số block dự kiến trong vòng một năm với block time được config ban đầu của Nexty chain là 2 giây.
+
+Số lượng reward sinh ra trong một năm được tính theo tỷ lệ sau đây:
+
+\begin{center}
+  \begin{tabular}{@{} cc @{}}
+    \hline
+    Year &  \% of circulating supply \\ 
+    \hline
+    1 & 10 \\ 
+    2 & 5 \\ 
+    3 & 2 \\ 
+    4 & 1 \\ 
+    5 & 1 \\     
+    ... & ... \\ 
+    ... & ... \\ 
+    ... & ... \\ 
+    n &  1 \\
+    \hline
+  \end{tabular}
+\end{center}
+
+\section{Cách thức chống SPAM hệ thống}
+
+Do transaction fee của Nexty là zero nên nếu không có phương thức chống Spam transaction hợp lý thì dễ dàng có thể bị tấn công bằng cách gửi liên tục nhiều giao dịch trong cùng 1 lúc gây ra nghẽn hệ thống.
+
+Chúng tôi đã có phương thức chống spam như sau:
+
+Nguyên tắc chung là hệ thống sẽ thu phí ở giao dịch đầu tiên với mức phí khoảng \textit{0.2 USD/1 tài khoản}, số tiền này sẽ được cộng vào giá trị reward của sealing round.
+Từ những giao dịch sau đó, hệ thống sẽ không thu phí giao dịch, nhưng yêu cầu các tài khoản đó phải chạy ứng dụng ví liên tục với số lượng block bằng \textit{[0.0015 * gas-used]} thì mới được gửi giao dịch tiếp theo.
+
+Ứng dụng ví của người dùng là một bản light client hay còn gọi là một block verifier (theo chuẩn light client protocol) có chức năng lưu lại những transaction của chính tài khoản đó, những tài khoản bên cạnh trong merkle tree, block number và các block header.
+Nhiệm vụ của light client là phải verify toàn bộ các thông tin giao dịch liên quan đến nó, cũng như xác thực tính đúng đắn của các block đã được sinh ra và block được sinh ra sau đó.
+Phải có 1 sự so sánh nếu blockchain bị can thiệp quá 15 block trở về trước thì phải có thông báo tới owner của ví đó rằng có thể hệ thống bị manipulated.
+Trong trường hợp đó sẽ cần truy cập cộng đồng chung để xem có lỗi nào xảy ra, đồng thời vote down đối với những authorized-sealers đã gây ra tình trạng sai sót đó.
+
+Với nguyên tắc này, một hành động spam phải bỏ ra một lượng tài nguyên hệ thống của nó lớn hơn khoảng 56.7 lần lượng tài nguyên của chain để xác nhận một giao dịch như vậy sẽ làm cho những đối tượng spammer tổn thất nhiều hơn và không còn ý định spam.
+
+Người dùng vẫn có quyền lựa chọn tạo transaction mất phí trong trường hợp họ không muốn duy trì block verifier như thế.
+
+Đối với những dApp, nó có thể tự cung cấp các hệ thống nodes để chịu phần gas của người dùng rồi sau đó có thể có hoặc không thu phí trên phần gas của người dùng tuỳ theo nhu cầu phát triển của dApp đó.
 

### 2018-06-06 Paper.tex
first draft English version of Nexty yellow paper

% !TEX encoding = UTF-8 Unicode

\documentclass[12pt,oneside]{amsart}
\usepackage{cancel}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[a4paper,width=165mm,top=20mm,bottom=25mm,includeheadfoot]{geometry}
\usepackage{array}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{natbib}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{mathtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{afterpage}
\usepackage{tikz}
\usepackage[bookmarks=true, unicode=true, pdftitle={Nexty Yellow Paper: a formal specification of Nexty, a zero transfer fee and instant transfer base on Ethereum blockchain}, pdfauthor={Thanh Dao / Ha Dang},pdfkeywords={Nexty, Ethereum, Yellow Paper, blockchain, virtual machine, cryptography, decentralised, singleton, transaction, generalised, zero transfer fee, instant transfer},pdfborder={0 0 0.5 [1 3]}]{hyperref}
%,pagebackref=true

\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}

\makeatletter
 \newcommand{\linkdest}[1]{\Hy@raisedlink{\hypertarget{#1}{}}}
\makeatother
\usepackage{seqsplit}

% For formatting
%\usepackage{underscore}
%\usepackage{lipsum} % to generate filler text for testing of document rendering
\usepackage[english]{babel}
\usepackage[autostyle]{csquotes}
\MakeOuterQuote{"}

\definecolor{pagecolor}{rgb}{1,0.98,0.9}

%Path relative to the main .tex file 
\graphicspath{ {./images/} }

\title{NEXTY: A CONSENSUS TO GET ZERO TRANSFER FEE AND INSTANT TRANSFER BLOCKCHAIN}
\author{
	Thanh Dao \& Ha Dang \\
	Co-founder/CTO @ Nexty Platform \\
	thanhdao@nexty.io / dvietha@gmail.com
}
\date{} % delete this line to display the current date

%%% BEGIN DOCUMENT
\begin{document}

\pagecolor{pagecolor}
\begin{abstract}
This is the detail technical paper of \href{https://nexty.io}{Nexty Platform}, focusing on describing the operation of a consensus protocol called Proof of Foundation. Proof of Foundation was inspired by the Proof of Authority introduced by \cite{clique} with improvement from \href{https://nexty.io}{Nexty Platform} by introducing a new confirmation system named \textbf{DCCS} - \textbf{D}ual \textbf{C}ryptocurrency \textbf{C}onfirmation \textbf{S}ystem to achieve a absolutely decentralized system and bring a highly incentive system for blockchain maintainers.
\end{abstract}

\maketitle

\setlength{\columnsep}{20pt}
\begin{multicols}{2}
%\tableofcontents

\section{Introduction}\label{sec:introduction}
In addition to {\small NTY} coin-base, {\small DCCS} has the secondary token named {\small NTF}. {\small NTF} is used for authorizing an account to become the maintainer/sealer of the confirmation system described detail in section \ref{sec:authorize}, as well as to calculate reward for block sealer. {\small NTF} token has total supply of $10,000,000$ and will be distributed for the first $100,000,000,000$ NTY holders that joined in ``Smart Staking'' program described detail in the white paper of \cite{smart-taking}. In the other words, {\small NTF} will be rewarded to the pioneers having a clear vision and a strong believe in \href{https://nexty.io}{Nexty Platform} in the future. That's the reason why we call the new consensus protocol as \textit{``Proof of Foundation''}. The power of \href{https://nexty.io}{Nexty Platform}, however, is not belong to {\small NTF} holders because they could be voted down by Nexty community if community found that {\small NTF} holders did any bad behavior of cheating, malicious or hand-shaking to make the network become centralize chain as well as using out-of-date source code. As a result, {\small NTF} holders have the only role as block sealer for Nexty blockchain and governed  by {\small NTY} community via decentralize voting system on a smart contract.

\section{How to authorize an account to become a block sealer}\label{sec:authorize}
The system will set up a configuration parameter to determine the minimum value, $min-ntf$, that an account need to have to become block sealer. Nexty will build and develop a smart contract, which allow {\small NTF} token holder, having enough token, to grant another account called ``executing-account'' to become the block sealer by setting ``authorized-sealer'' state in the smart contract with the value equal to address of {\small NTF} holder. If an address already has an ``authorized-sealer'' value, it can not receive authorization from another NTF holder until the NTF holder has made the withdrawal it from ``authorized-sealer''. The ``authorized-sealer'' list will be determined at the check point block of each sealing round by reading state from the smart contract at that point of time. If in the current sealing round, any ``authorized-sealer'' does not perform at least one sealing activity, the ``authorized-sealer'' value will be withdrawn to its {\small NTF} holder by updating the state of the smart contract at the checkpoint block number of the next sealing round and of course that ``authorized-sealer'' will not be involved in the next sealing rounds until it will be authorized to become ``authorized-sealer'' again.

\section{Block sealing mechanism}\label{sec:sealing}
The {\small DCCS} block sealing mechanism will be implemented  as in following steps. Firstly, the sealers will be numbered from $1$ to $n$ (called ``sealing-id'') randomly at the beginning of each sealing round; in which, $n$ is the number of registered ``authorized-sealer'' and is determined by the state of the smart contract at the \textit{checkpoint block number} of the corresponding sealing round. To ensure the randomness of ``sealing-id'', the numbering is calculated by a hash,  $\boldsymbol{\xi_{\mathrm{k}}}$, as following formula when starting a new sealing round.

\begin{equation}
\xi_{\mathrm{k}} \equiv \texttt{\small KEC}(\mathbf{block}, \mathbf{\Lambda_{\mathrm{k}}})
\end{equation}

\begin{description}
\item[block] is the first block number, a.k.a  \textit{checkpoint block number} of the sealing round.
\item[$\Lambda_{\mathrm{k}}$] is the address that the {\small NTF} holder has set as ``authorized-sealer'' in the smart contract.
\item[\texttt{\small KEC}] is the \textbf{\small {SHA-3 Keccak-512}} hash function of any input.
\end{description}

After that, the ``sealing-id'' of each authorized-sealer will be taken by the position of \textit{sealing hash}, $\boldsymbol{\xi_k}$, in the array $(\xi_{\mathrm{1}}, \xi_{\mathrm{2}}, ..., \xi_{\mathrm{n}})$, ascending ordered by the \textit{sealing hash}.

To ensure performance of the system, the ``sealing-id'' of the all authorized sealers will be snapshot only once from the smart contract state at the \textit{checkpoint block number} of each sealing round and stored in the local database as well as in \textbf{lru cache} of each node.

\subsection{Scenario 1}\label{ch:scenario_1} If sealing node is not in recent sealers. The node will determine whether it's the in-turn sealer for the next block or not, according to the following formula:

\begin{equation}\label{eq:sigma}
\sigma_{\mathrm{k}} \equiv (\nu - \mathbf{block}) \ \ \ \mathbf{mod} \ \ \ \Pi
\end{equation}

\begin{description}
\item[$\nu$] is the current block number that is being sealed.
\item[block] is the first block number, a.k.a \textit{checkpoint block number}, of the current sealing round.
\item[$\Pi$] total number of authorized sealer reading from smart contract state at the \textit{checkpoint block} of the current sealing round.
\end{description}

If the remainder $\sigma_{\mathrm{k}}$ equal to ``sealing-id'' of the node, then that node has the right to seal block immediately. Otherwise, at each of the next block, sealing nodes have to wait a course of time, $\psi_{\mathrm{k}}$, which is calculated by the formula:

\begin{eqnarray}
\alpha = 001.387978000 \\
\beta = 000.002313279 \\
\gamma = 000.004626590 \\
\delta = 199.999400000
\end{eqnarray}

\begin{equation}\label{eq:psi}
\psi_{\mathrm{k}} \equiv \sum_{i=1}^{\zeta_\mathrm{k}} \mathbf{floor}(\frac{\alpha}{\beta*i+\gamma} + \delta)
\end{equation}

\subsection{Scenario 2}\label{ch:scenario_2} If sealing node is in recent sealers

In this scenario, sealers still can continue to seal block, but they have to wait a period of time longer than all other sealers, not in recent sealers. This is procedure to ensure that the system can still generate blocks, even when there is only one sealer, but the chain be suspended for a very long time. The waiting time ranges from $3$ - $30$ minutes, if there are $1,000$ - $10,000$ authorized sealers and only one or few active sealers.

Waiting time, $\psi_{\mathrm{k}}$,  is caculated by the following formula:

\begin{eqnarray}
\alpha = 001.387978000 \\
\beta = 000.002313279 \\
\gamma = 000.004626590 \\
\delta = 199.999400000
\end{eqnarray}

\begin{multline}\label{eq:psi_2}
\psi_{\mathrm{k}} \equiv \sum_{i=1}^{n} \mathbf{floor}(\frac{\alpha}{\beta*i+\gamma} + \delta) \\ 
+ \sum_{i=1}^{\zeta_\mathrm{k}} \mathbf{floor}(\frac{\alpha}{\beta*i+\gamma} + \delta)
\end{multline}

The coefficients of the above formula are assumed as following. The sealing node having ``sealing-id'' equal to $\sigma_{\mathrm{k}}$, calculated by formula $\eqref{eq:sigma}$, will have the priority to seal block before 400ms, the next sealing node will have the priority to seal block before 350ms, then 320ms,... till the final sealing node with approximately to 200ms. Its graph corresponds to the function $\texttt{\small y} = \frac{a} {(b * x + c)} + \texttt{\small d}$

To estimate values for the parameters, we use curve fitting method to find relatives coefficient in the website \href{https://mycurvefit.com/}{My Curve Fit} with the variance \footnote{R² is 1 minus the ratio of sum of the squares of the residuals divided by the sum of the squares of the differences between Y fit and the mean Y value} $\approx 1$.
\\
\\
\includegraphics[width=0.48\textwidth, height=4cm]{curve-fit}
\\
A sealing round of all authorized sealer is called an epoch. Epoch will have various length, depends on the number of sealers in a chain of each sealing round.

A sealer who is worried about being withdrawn authorized sealer to {\small NTF} holder might not participate in sealing activity in a sealing round, but still occupies the right to seal block at some point earlier than his/her sealing turn; causes welter and racing for sealing block. By calculating the fixed waiting time for each sealer, using formula $\eqref{eq:psi}$ or $\eqref{eq:psi_2}$, consensus are able to keep track of sealer. Nexty blockchain will verify a block, sealed by an ``authorized-sealer'', by figuring out if the generating time of ``authorized-sealer''’s block is smaller than it's waiting time.

\section{Block sealer reward calculation}

After each sealing round, reward value $\Re$ of each sealer will be calculated as the minimum value of the total reward divided by the active sealers according to the proportion of {\small NTF} they have on the total {\small NTF} of the sealers who participated in the seal.

\begin{eqnarray}
\theta = \frac{\Omega}{N} \\
\phi = \frac{\Upsilon_{NTF}}{\Xi_{NTF}}
\end{eqnarray}

\begin{equation}\label{eq:re}
\Re \equiv \min(\theta, \phi)
\end{equation}

\begin{description}
\item[$\Omega$] total reward
\item[N] total number of active sealer of the current sealing round
\item[$\Upsilon_{NTF}$] amount of NTF token that the owner of active sealer is holding
\item[$\Xi_{NTF}$] total amount of NTF token that all active sealer are holding
\end{description}

According to formula $\eqref{eq:re}$, people who own {\small NTF} in a natural way will divide his/her {\small NTF} into many wallets in order to equip multiple sealers, instead of building only one sealer and spend too much  {\small NTF} on it. This ensures the Nexty chain will have sufficiently large number of nodes to make Nexty chain become highly decentralization, stability and robust.

Total reward $\Re$ is the amount of {\small NTF} was produced after each sealing round, calculated as \textit{[reward generated in one block]} * \textit{[number of blocks generated in that sealing round]}.

The number of rewards generated for a block is equal to the number of rewards per year divided by $\mathbf{15,768,000}$, the expected number of block within one year (initial configuration of block time is 2 seconds).

The amount of rewards in a year is calculated in the following proportions:

\begin{center}
  \begin{tabular}{@{} cc @{}}
    \hline
    Year &  \% of circulating supply \\ 
    \hline
    1 & 10 \\ 
    2 & 5 \\ 
    3 & 2 \\ 
    4 & 1 \\ 
    5 & 1 \\     
    ... & ... \\ 
    ... & ... \\ 
    ... & ... \\ 
    n &  1 \\
    \hline
  \end{tabular}
\end{center}

\section{Anti-SPAM}\label{sec:spam}

Since Nexty's transaction fee is zero, if there is no proper anti-spam protection, it can easily be attacked by sending multiple transactions simultaneously, causing system blockage.

We have the following anti-spam methods:

The general rule is that the system will charge the first transaction with a fee of \textit{0.2 per account}, which will be added to the reward value of the sealing round. From subsequent transactions, the system will not charge transaction fees, but requires those accounts to run a continuous wallet application with the number of blocks equal to \textit{[0.0015 * gas-used]}, after that, they will be able to send next transactions.

Mobile wallet app is a light client version, as known as a block verifier (based on light client protocol standard) which has the ability to save transactions of the it's own account and contiguous accounts in \textit{Merkle Tree} and block headers. The responsibility of a light client is to verify all transactional information related to it, as well as validate the blocks generated afterward. There should be a comparison if the blockchain is interfered with more than 15 blocks backwards, then notify to the owner of the wallet that the system might be manipulated. In some case, community must be accessed to see if any errors occurred, and vote down on the ``authorized-sealers'' that caused the malicious data. Under this rule, a spam action that spends more than 56.7 times the amount of resources on the chain to confirm such a transaction. This results in a loss in resources for spammers and therefore, ruins their intention of spamming.

Users still have the option of creating a charged transaction in case they do not want to maintain block verifier.

For \textbf{{\small {dApp}}}, it can provide its own system of nodes to withstand the user's gas and then there may or may not be a charge on the user's gas depending on the development needs of the \textbf{{\small {dApp}}}.

\bibliographystyle{plainnat}
\bibliography{Biblio}

\end{multicols}
\end{document}

### 2018-06-18 Paper.tex
Fix typo and update to nexty.io email

@@
 	Co-founder/CTO @ Nexty Platform \\
-	thanhdao@nexty.io / dvietha@gmail.com
+	thanhdao@nexty.io / hadang@nexty.io
 }
@@
 
-Total reward $\Re$ is the amount of {\small NTF} was produced after each sealing round, calculated as \textit{[reward generated in one block]} * \textit{[number of blocks generated in that sealing round]}.
+Total reward $\Omega$ is the amount of {\small NTF} was produced after each sealing round, calculated as \textit{[reward generated in one block]} * \textit{[number of blocks generated in that sealing round]}.
 

### 2018-08-05 Paper.tex
Update some typos

@@
 This is the detail technical paper of \href{https://nexty.io}{Nexty Platform}, focusing on describing the operation of a consensus protocol called Proof of Foundation.
-Proof of Foundation was inspired by the Proof of Authority introduced by \cite{clique} with improvement from \href{https://nexty.io}{Nexty Platform} by introducing a new confirmation system named \textbf{DCCS} - \textbf{D}ual \textbf{C}ryptocurrency \textbf{C}onfirmation \textbf{S}ystem to achieve a absolutely decentralized system and bring a highly incentive system for blockchain maintainers.
+Proof of Foundation was inspired by the Proof of Authority introduced by \cite{clique} with improvement from \href{https://nexty.io}{Nexty Platform} by introducing a new confirmation system named \textbf{DCCS} - \textbf{D}ual \textbf{C}ryptocurrency \textbf{C}onfirmation \textbf{S}ystem to achieve a decentralized system and bring a highly incentive system for blockchain maintainers.
 \end{abstract}
@@
 The {\small DCCS} block sealing mechanism will be implemented  as in following steps.
-Firstly, the sealers will be numbered from $1$ to $n$ (called ``sealing-id'') randomly at the beginning of each sealing round; in which, $n$ is the number of registered ``authorized-sealer'' and is determined by the state of the smart contract at the \textit{checkpoint block number} of the corresponding sealing round.
+Firstly, the sealers will be numbered from $0$ to $n - 1$ (called ``sealing-id'') randomly at the beginning of each sealing round; in which, $n$ is the number of registered ``authorized-sealer'' and is determined by the state of the smart contract at the \textit{checkpoint block number} of the corresponding sealing round.
 To ensure the randomness of ``sealing-id'', the numbering is calculated by a hash,  $\boldsymbol{\xi_{\mathrm{k}}}$, as following formula when starting a new sealing round.
@@
 
-After that, the ``sealing-id'' of each authorized-sealer will be taken by the position of \textit{sealing hash}, $\boldsymbol{\xi_k}$, in the array $(\xi_{\mathrm{1}}, \xi_{\mathrm{2}}, ..., \xi_{\mathrm{n}})$, ascending ordered by the \textit{sealing hash}.
+After that, the ``sealing-id'' of each authorized-sealer will be taken by the position of \textit{sealing hash}, $\boldsymbol{\xi_k}$, in the array $(\xi_{\mathrm{0}}, \xi_{\mathrm{1}}, ..., \xi_{\mathrm{n-1}})$, ascending ordered by the \textit{sealing hash}.
 

### 2019-05-21 Paper.tex
update technical paper

@@
 \section{How to authorize an account to become a block sealer}\label{sec:authorize}
-The system will set up a configuration parameter to determine the minimum value, $min-ntf$, that an account need to have to become block sealer.
-Nexty will build and develop a smart contract, which allow {\small NTF} token holder, having enough token, to grant another account called ``executing-account'' to become the block sealer by setting ``authorized-sealer'' state in the smart contract with the value equal to address of {\small NTF} holder.
+The system will set up a configuration parameter to define the minimum value, $\mathbf{50,000}$ {\small NTF}, that an account need to deposit into Nexty governance smart contract to become a block sealer.
+Nexty will build and develop a governance smart contract, which allow {\small NTF} token holder, having enough token, to grant another account called ``executing-account'' to become the block sealer by setting ``authorized-sealer'' state in the smart contract with the value equal to address of {\small NTF} holder.
 If an address already has an ``authorized-sealer'' value, it can not receive authorization from another NTF holder until the NTF holder has made the withdrawal it from ``authorized-sealer''.
-The ``authorized-sealer'' list will be determined at the check point block of each sealing round by reading state from the smart contract at that point of time.
-If in the current sealing round, any ``authorized-sealer'' does not perform at least one sealing activity, the ``authorized-sealer'' value will be withdrawn to its {\small NTF} holder by updating the state of the smart contract at the checkpoint block number of the next sealing round and of course that ``authorized-sealer'' will not be involved in the next sealing rounds until it will be authorized to become ``authorized-sealer'' again.
+The ``authorized-sealer'' list will be determined at the check point block of each epoch by reading canonical state from the smart contract at that point of time.
+If in the current epoch, any ``authorized-sealer'' does not perform at least one sealing activity, the ``authorized-sealer'' value will be withdrawn to its {\small NTF} holder by updating the state of the smart contract at the checkpoint block number of the next epoch and of course that ``authorized-sealer'' will not be involved in the next epoch until it will be authorized to become ``authorized-sealer'' again.
+We will introduce more detail about this on Nexty governance section later \ref{sec:governace}.
 
@@
 The {\small DCCS} block sealing mechanism will be implemented  as in following steps.
-Firstly, the sealers will be numbered from $0$ to $n - 1$ (called ``sealing-id'') randomly at the beginning of each sealing round; in which, $n$ is the number of registered ``authorized-sealer'' and is determined by the state of the smart contract at the \textit{checkpoint block number} of the corresponding sealing round.
-To ensure the randomness of ``sealing-id'', the numbering is calculated by a hash,  $\boldsymbol{\xi_{\mathrm{k}}}$, as following formula when starting a new sealing round.
+Firstly, the sealers will be numbered from $0$ to $n - 1$ (called ``sealing-id'') randomly at the beginning of each epoch; in which, $n$ is the number of registered ``authorized-sealer'' and is determined by the state of the governance smart contract at the canonical chain from \textit{checkpoint block number} of the corresponding epoch.
+To ensure the randomness of ``sealing-id'', the numbering is calculated by a hash,  $\boldsymbol{\xi_{\mathrm{k}}}$, as following formula when starting a new epoch.
 
@@
 \begin{description}
-\item[block] is the first block number, a.k.a  \textit{checkpoint block number} of the sealing round.
-\item[$\Lambda_{\mathrm{k}}$] is the address that the {\small NTF} holder has set as ``authorized-sealer'' in the smart contract.
+\item[block] is the canonical block number from the \textit{checkpoint block number} of the epoch. a.k.a \textit{checkpoint block number} - 7
+\item[$\Lambda_{\mathrm{k}}$] is the address that the {\small NTF} holder has set as ``authorized-sealer'' in the governance smart contract.
 \item[\texttt{\small KEC}] is the \textbf{\small {SHA-3 Keccak-512}} hash function of any input.
@@
 
-To ensure performance of the system, the ``sealing-id'' of the all authorized sealers will be snapshot only once from the smart contract state at the \textit{checkpoint block number} of each sealing round and stored in the local database as well as in \textbf{lru cache} of each node.
+To ensure performance of the system, the ``sealing-id'' of the all authorized sealers will be snapshot only once from the smart contract state at the canonical chain from \textit{checkpoint block number} of each epoch and stored in the local database as well as in \textbf{lru cache} of each node.
 
-\subsection{Scenario 1}\label{ch:scenario_1} If sealing node is not in recent sealers.
-The node will determine whether it's the in-turn sealer for the next block or not, according to the following formula:
+If sealing node is not in recent sealers. The node will determine whether it's the in-turn sealer for the next block or not, according to the following formula:
 
@@
 \item[$\nu$] is the current block number that is being sealed.
-\item[block] is the first block number, a.k.a \textit{checkpoint block number}, of the current sealing round.
-\item[$\Pi$] total number of authorized sealer reading from smart contract state at the \textit{checkpoint block} of the current sealing round.
+\item[block] is the canonical block number from \textit{checkpoint block number}, of the current epoch.
+\item[$\Pi$] total number of authorized sealer reading from smart contract state at the canonical block from \textit{checkpoint block} of the current epoch.
 \end{description}
 
-If the remainder $\sigma_{\mathrm{k}}$ equal to ``sealing-id'' of the node, then that node has the right to seal block immediately.
-Otherwise, at each of the next block, sealing nodes have to wait a course of time, $\psi_{\mathrm{k}}$, which is calculated by the formula:
+If the remainder $\sigma_{\mathrm{k}}$ equal to ``sealing-id'' of the node, then that node has in-turn sealer and seal block immediately with highest \textit{difficulty}.
+Otherwise, nodes will wait a period of time, $\psi_{\mathrm{k}}$, which is calculated by the formula:
 
@@
 \gamma = 000.004626590 \\
-\delta = 199.999400000
+\delta = 499.999400000
 \end{eqnarray}
@@
 
-\subsection{Scenario 2}\label{ch:scenario_2} If sealing node is in recent sealers
-
-In this scenario, sealers still can continue to seal block, but they have to wait a period of time longer than all other sealers, not in recent sealers.
-This is procedure to ensure that the system can still generate blocks, even when there is only one sealer, but the chain be suspended for a very long time.
-The waiting time ranges from $3$ - $30$ minutes, if there are $1,000$ - $10,000$ authorized sealers and only one or few active sealers.
-
-Waiting time, $\psi_{\mathrm{k}}$,  is caculated by the following formula:
-
-\begin{eqnarray}
-\alpha = 001.387978000 \\
-\beta = 000.002313279 \\
-\gamma = 000.004626590 \\
-\delta = 199.999400000
-\end{eqnarray}
-
-\begin{multline}\label{eq:psi_2}
-\psi_{\mathrm{k}} \equiv \sum_{i=1}^{n} \mathbf{floor}(\frac{\alpha}{\beta*i+\gamma} + \delta) \\ 
-+ \sum_{i=1}^{\zeta_\mathrm{k}} \mathbf{floor}(\frac{\alpha}{\beta*i+\gamma} + \delta)
-\end{multline}
-
 The coefficients of the above formula are assumed as following.
-The sealing node having ``sealing-id'' equal to $\sigma_{\mathrm{k}}$, calculated by formula $\eqref{eq:sigma}$, will have the priority to seal block before 400ms, the next sealing node will have the priority to seal block before 350ms, then 320ms,...
-till the final sealing node with approximately to 200ms.
+The sealing node having ``sealing-id'' equal to $\sigma_{\mathrm{k}}$, calculated by formula $\eqref{eq:sigma}$, will have the priority to seal block before 400ms, the next sealing node will have the priority to seal block before 850ms, then 820ms,...
+till the final sealing node with approximately to 500ms.
 Its graph corresponds to the function $\texttt{\small y} = \frac{a} {(b * x + c)} + \texttt{\small d}$
@@
 \\
-A sealing round of all authorized sealer is called an epoch. Epoch will have various length, depends on the number of sealers in a chain of each sealing round.
 
-A sealer who is worried about being withdrawn authorized sealer to {\small NTF} holder might not participate in sealing activity in a sealing round, but still occupies the right to seal block at some point earlier than his/her sealing turn; causes welter and racing for sealing block.
-By calculating the fixed waiting time for each sealer, using formula $\eqref{eq:psi}$ or $\eqref{eq:psi_2}$, consensus are able to keep track of sealer.
-Nexty blockchain will verify a block, sealed by an ``authorized-sealer'', by figuring out if the generating time of ``authorized-sealer''’s block is smaller than it's waiting time.
+The difficulty of sealing block for \textit{n} sealers will be calculated in the formula \eqref{eq:difficulty} as below
+
+\begin{equation}\label{eq:difficulty}
+    d(i) \equiv
+    \begin{cases}
+    	n	& \quad \text{if } sealer \text{ is in-turn}\\
+	n - k_i & \quad \text{if } sealer \text{ is out-turn}
+    \end{cases}
+\end{equation}
+
+${k_i}$ is the relative position of \textit{out-turn} sealer ${i^{th}}$ to the position of \textit{in-turn} sealer in the current sealing order list.
+
+\section{Nexty Governance}\label{sec:governace}
+
+This section will describe detail implementation of registration smart contract deployed at address \textbf{0x12345} using for consensus system.
+
+\subsection{Terminology}
+
+\begin{description}
+\item[sealer] a participant in the Nexty consensus system. You can become one by depositing {\small DEPOSIT\_SIZE} {\small NTFs} into the Nexty mechanism.
+\item[active sealer set] those sealer who are currently participating, and which the Nexty mechanism looks to seal blocks and other consensus objects.
+\item[withdrawal period] number of epochs between a sealer exit and the sealer balance being withdraw-able.
+\item[coinbase] the account address that sealer will use to sign when sealing block.
+\item[registration contract] a smart contract for handling Nexty consensus mechanism.
+\end{description}
+
+\subsection{Constants}
+
+\begin{center}
+  \begin{tabular}{{l|l|l}}
+    \hline
+    Constant & Value & Unit \\
+    \hline
+    BLOCK\_TIME & ${2}$ & seconds \\
+    EPOCH\_LENGTH & ${3,000}$ & blocks \\
+    DEPOSIT\_SIZE & ${50,000}$ & {\small NTFs} \\
+    WITHDRAWAL\_PERIOD & ${30,000}$ & blocks \\
+    \hline
+  \end{tabular}
+\end{center}
+
+\subsection{Sealer status codes}
+
+\begin{description}
+\item[PENDING\_ACTIVE = 0] Sealer deposited enough {\small NTFs} into registration contract successfully. 
+\item[ACTIVE = 1] Sealer send request to become a sealer and added into activation sealer set successfully.
+\item[PENDING\_WITHDRAW = 2] Sealer send request to exit from activation sealer set successfully. Sealer casted out of activation sealer set.
+\item[WITHDRAWN = 3] Sealer already withdrawn their deposit {\small NTFs} successfully. They can only make withdrawal after withdrawal period.
+\item[PENALIZED = 127] Sealer marked as penalized node (update by consensus or voting result via dapp) and cannot become active sealer and cannot withdraw balance neither.
+\end{description}
+
+\subsection{Nexty chain registration contract}
+A registration contract is added to the Nexty chain to deposit {\small NTF} and activation sealer set management. It has some below basic functions:
+
+\subsubsection{Sealer Operations}
+\begin{description}
+\item[Deposit] Transfer the {\small NTF} from token holder to registration contract. Sealer might have to approve contract to transfer an amount of {\small NTF} before calling this function.
+\item[Join] To allow deposited {\small NTF} participate joining in as sealer.
+Participate already must deposit enough {\small NTF} via \textbf{Deposit} function.
+it takes \textbf{coinbase} as parameter.
+\item[Exit] Request to exit out of activation sealer set.	
+\item[Withdraw] To withdraw sealer’s {\small NTF} balance when they already exited and after \textbf{withdrawal period}.
+\end{description}
+
+\subsubsection{Sealer Record}
+\begin{description}
+\item[Coinbase address] sealer’s coinbase address to sign when sealing block
+\item[Balance] the total amount of {\small NTF} that sealer has deposited
+\item[Status] Sealer status code
+\item[Requested Block Number] The block number at which sealer send request to exit out of activation sealer set.
+\end{description}
+
+\subsection{How to become a sealer}
+\begin{enumerate}
+\item A participant should deposit at least {\small DEPOSIT\_SIZE} {\small NTFs} into registration contract, a.k.a the network have maximum ~200 candidate nodes can become a sealer.
+Sealer status will be set to {\small PENDING\_ACTIVE}.
+\item A participant need to set their \textbf{coinbase} to seal the block and receive reward on their equivalent {\small NTF} token holder address.
+\item A participant call registration contract method to become sealer. Sealer status be updated to {\small ACTIVE}.
+\item At next checkpoint of the epoch, sealer request be cast and the sealer be added into consensus \textbf{activation sealer set}.
+\end{enumerate}
+
+\subsection{How to exit from activation sealer and NTF withdrawal}
+\begin{enumerate}
+\item Sealer call registration contract method to request for exiting from activation sealer set and sealer status be updated to {\small PENDING\_WITHDRAW} but still in the activation sealer set on the current epoch.
+\item At next checkpoint of the epoch, sealer exit request be cast and the sealer be removed out of \textbf{activation sealer set}. 
+\item Sealer can call register contract method to withdrawn their deposited {\small NTF} after a withdrawal period.
+The sealer status be changed to {\small WITHDRAWN} after sealer withdraw the {\small NTFs} successfully.
+\end{enumerate}
+
+\subsection{Sealer authorization}
+When a node starting with --${mine}$ option then they need to unlock the unique \textbf{coinbase} account setting in the activation sealer set.
+If the \textbf{coinbase} was not found in the current epoch \textbf{activation sealer set} then unauthorization error will be throw and it cannot start mining but they still can continue to sync block preparing for sealing later.
 
@@
 
-After each sealing round, reward value $\Re$ of each sealer will be calculated as the minimum value of the total reward divided by the active sealers according to the proportion of {\small NTF} they have on the total {\small NTF} of the sealers who participated in the seal.
-
-\begin{eqnarray}
-\theta = \frac{\Omega}{N} \\
-\phi = \frac{\Upsilon_{NTF}}{\Xi_{NTF}}
-\end{eqnarray}
-
-\begin{equation}\label{eq:re}
-\Re \equiv \min(\theta, \phi)
-\end{equation}
-
-\begin{description}
-\item[$\Omega$] total reward
-\item[N] total number of active sealer of the current sealing round
-\item[$\Upsilon_{NTF}$] amount of NTF token that the owner of active sealer is holding
-\item[$\Xi_{NTF}$] total amount of NTF token that all active sealer are holding
-\end{description}
-
-According to formula $\eqref{eq:re}$, people who own {\small NTF} in a natural way will divide his/her {\small NTF} into many wallets in order to equip multiple sealers, instead of building only one sealer and spend too much  {\small NTF} on it.
-This ensures the Nexty chain will have sufficiently large number of nodes to make Nexty chain become highly decentralization, stability and robust.
-
-Total reward $\Omega$ is the amount of {\small NTF} was produced after each sealing round, calculated as \textit{[reward generated in one block]} * \textit{[number of blocks generated in that sealing round]}.
-
-The number of rewards generated for a block is equal to the number of rewards per year divided by $\mathbf{15,768,000}$, the expected number of block within one year (initial configuration of block time is 2 seconds).
-
-The amount of rewards in a year is calculated in the following proportions:
+Reward will be added immediately into sealer’s account balance after sealing a block.
+The reward for a block is equal to the number of rewards per year divided by $\mathbf{15,768,000}$, the expected number of block within one year (initial configuration of block time is 2 seconds).
+The amount of rewards of each block sealing in a specific year is calculated in the following proportions:
 
 \begin{center}
-  \begin{tabular}{@{} cc @{}}
+  \begin{tabular}{c | l | l}
     \hline
-    Year &  \% of circulating supply \\ 
+    Year &  \% of total supply & Reward/Blk\\ 
     \hline
-    1 & 10 \\ 
-    2 & 5 \\ 
-    3 & 2 \\ 
-    4 & 1 \\ 
-    5 & 1 \\     
-    ... & ... \\ 
-    ... & ... \\ 
-    ... & ... \\ 
-    n &  1 \\
+    1 & 10.000 & 1,141\\ 
+    2 & 5.000 & 627 \\ 
+    3 & 2.500 & 329 \\ 
+    4 & 1.250 & 169 \\ 
+    5 & 0.625 & 85 \\
+    6 & 0.500 & 69 \\
+    ... & 0.500 & ... \\
+    ... & 0.500 & ... \\ 
+    n & 0.500 & ... \\
     \hline

### 2019-06-16 Paper.tex

@@
 The power of \href{https://nexty.io}{Nexty Platform}, however, is not belong to {\small NTF} holders because they could be voted down by Nexty community if community found that {\small NTF} holders did any bad behavior of cheating, malicious or hand-shaking to make the network become centralize chain as well as using out-of-date source code.
-As a result, {\small NTF} holders have the only role as block sealer for Nexty blockchain and governed  by {\small NTY} community via decentralize voting system on a smart contract.
+As a result, {\small NTF} holders have the only role as block sealer for Nexty blockchain and governed  by {\small NTY} community via decentralize voting system.
 
@@
 The ``authorized-sealer'' list will be determined at the check point block of each epoch by reading canonical state from the smart contract at that point of time.
-If in the current epoch, any ``authorized-sealer'' does not perform at least one sealing activity, the ``authorized-sealer'' value will be withdrawn to its {\small NTF} holder by updating the state of the smart contract at the checkpoint block number of the next epoch and of course that ``authorized-sealer'' will not be involved in the next epoch until it will be authorized to become ``authorized-sealer'' again.
+If in the last three epochs, any ``authorized-sealer'' does not perform at least one sealing activity, the ``authorized-sealer'' value will slash by updating the state of the smart contract at the checkpoint block number of the next epoch and of course that ``authorized-sealer'' will not be involved in the next epoch until it will be authorized to become ``authorized-sealer'' again via community voting dapp.
 We will introduce more detail about this on Nexty governance section later \ref{sec:governace}.
@@
 
+\subsection{Penalized}
+
+At the checkpoint of each epoch, consensus will collect the data from the chain to find out any sealers that didn't seal any blocks 3 epochs in a row.
+Then to ensure the network healthy, those sealers will be removed out of the \textbf{activation sealer set} in the new epoch and mark sealer's status as {\small PENALIZED}.
+Because, offline sealers may due to the nature of unstable global network and dis-continue infrastructure service that out of control of the sealers.
+Then all {\small PENALIZED} sealers then can be unlock the slash after voting up by {\small NTY} community via a specific voting smart contract as well as dapp.
+
 \section{Block sealer reward calculation}
@@
 
-Since Nexty's transaction fee is zero, if there is no proper anti-spam protection, it can easily be attacked by sending multiple transactions simultaneously, causing system blockage.
+\subsection{Most Frequency Use}\label{sec:mfu}
 
-We have the following anti-spam methods:
+In Nexty blockchain, we allow end user to perform transaction with zero fee.
+Therefore, we introduce a mechanism to priority transactions base on some other factors other than using only the \textbf{gasprice}.
+The first factor is similar to stamina, each account will have a \textbf{most frequency use} state.
+whenever, transaction from account to include in the block then the \textbf{most frequency use}, ${\Delta_{new}}$, will be update as following formula.
 
-The general rule is that the system will charge the first transaction with a fee of \textit{0.2 per account}, which will be added to the reward value of the sealing round.
-From subsequent transactions, the system will not charge transaction fees, but requires those accounts to run a continuous wallet application with the number of blocks equal to \textit{[0.0015 * gas-used]}, after that, they will be able to send next transactions.
+\begin{equation}
+	{\Delta_{new}}  = {\Delta_{old}} + max(1, \frac{(block - {\Delta_{old}}) * GasUsed}{3 * 21000})
+\end{equation}
 
-Mobile wallet app is a light client version, as known as a block verifier (based on light client protocol standard) which has the ability to save transactions of the it's own account and contiguous accounts in \textit{Merkle Tree} and block headers.
-The responsibility of a light client is to verify all transactional information related to it, as well as validate the blocks generated afterward.
-There should be a comparison if the blockchain is interfered with more than 15 blocks backwards, then notify to the owner of the wallet that the system might be manipulated.
-In some case, community must be accessed to see if any errors occurred, and vote down on the ``authorized-sealers'' that caused the malicious data.
-Under this rule, a spam action that spends more than 56.7 times the amount of resources on the chain to confirm such a transaction.
-This results in a loss in resources for spammers and therefore, ruins their intention of spamming.
+\begin{description}
+\item[block] is the block number that transaction was include.
+\item[GasUsed] gas used by the transaction
+\end{description}
 
-Users still have the option of creating a charged transaction in case they do not want to maintain block verifier.
+Ideally, the higher \textbf{most frequency use} value, the less priority of the account's transaction in the transaction pool.
+And each time an account perform the transaction, \textbf{most frequency use} value of that account will be increase; as a result, the next transaction of the same account will be less priority.
+And to avoid spam by new account, the \textbf{most frequency use} of a new account will be the block number of the account's first transaction.
 
-For \textbf{{\small {dApp}}}, it can provide its own system of nodes to withstand the user's gas and then there may or may not be a charge on the user's gas depending on the development needs of the \textbf{{\small {dApp}}}.
+\subsection{Transaction Parity}\label{sec:parity}
+
+Along with  \textbf{most frequency use} above, we introduce a new factor to decide the priority of the transaction called \textbf{parity} and will be calculated as below
+
+\begin{equation}\label{eq:parity}
+{\rho_t} = {\Delta_{act}} + \frac{TxGasLimit}{21000} - \frac{TxGasPrice}{ParityLimit}
+\end{equation}
+
+\begin{description}
+\item[${\Delta_{act}}$] \textbf{most frequency use} value of the account when perform transaction
+\item[TxGasLimit] transaction gas limit, the higher gas limit transaction, the less priority
+\item[TxGasPrice] transaction gas price, can be input arbitrarily by user. User can put higher gas price if they want to make transaction be confirmed faster.
+\item[ParityLimit] parity limit be configured by miner, the higher parity limit, the less transaction gas price effect into the overall parity value, ${\rho_t}$
+\end{description}
+
+Overall, a transaction was include in the miner's txpool with priority base on the value of transaction parity calculated in formula \eqref{eq:parity} then even though Nexty allow user to send tnx with zero fee but sealer's pool can arbitrarily setting parameters to utilize the sealer's resource for anti spamming transaction and ensure normal user's transaction to be proceed without delay.
+
+\subsection{Transaction Proof of Work}
+In the near future, when the Nexty chain will be fulfilled or be spammed by unmeaning transactions, we will introduce a mechanism to avoid those kind of problem by enforcing user to send a proof of mini work along with the transaction, the transaction with valid proof will be sealed in the block with highest priority.
+To make a better user experience and adoption, we will develop this feature in user wallet; when the transaction confirmation is too slow, wallet will allow user to take action to do transaction proof of work on their wallet before sending transaction.
 
